---
title: "Homework 1"
author: Minjie Bao
output: github_document
---

This is my solution to HW1.

```{r}
library(tidyverse)
```

## Problem 1

#### Create a data frame from with the specified elements.

```{r}
prob1_df =
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp>0,
    char_vec = c("a","b","c","d","e","f","g","h","i","j"),
    factor_vec = factor(c("low","low","low","mod","mod","mod","mod","high","high","high"))
)
```

#### Take the mean of each variable in my data frame.

```{r}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```

I can take the mean of numbers and logical but not character or factor.

```{r}
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```


#### convert the logical vector to different data types and multiply the random sample by the result

```{r}
as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.factor(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.numeric(as.factor(pull(prob1_df, samp_gt_0))) * pull(prob1_df, samp)
```


## Problem 2

#### load penguins dataset.

```{r}
data("penguins", package = "palmerpenguins")
penguins
```

#### part1 : the data in this dataset (names / values of important variables), the size of the dataset, the mean flipper length

```{r}
ls(penguins)
summary(penguins)

nrow(penguins)
ncol(penguins)
size = nrow(penguins) * ncol(penguins)
print(size)

mean(penguins$flipper_length_mm, na.rm = TRUE)

```
Explanation of the codes:

From ls(penguins), we can see that there are 8 variables: "bill_depth_mm", "bill_length_mm", "body_mass_g", "flipper_length_mm" "island", "sex", "species", "year".

From summary (penguins), we can see the 5 number summary and mean of each variable.

The size of the dataset is 2752.

The mean of flipper length is 200.9152.


 #### part 2 : scatterplot and ggsave

```{r}
plot_df = tibble(x = pull(penguins,bill_length_mm), y = pull(penguins,flipper_length_mm), species=pull(penguins,species))
view(plot_df)
ggplot(plot_df, aes(x = x, y = y, color=species)) + geom_point()
ggsave("scatter_plot.pdf", height = 4, width = 6)
```



